Standard Candle Cosmology With Incomplete Spectroscopic Classification

### 2015-10-23 doc/article.tex
new "done" version

\section{DES SN Survey Model}
\label{snIamodel:sec}
\subsection{Model}
This Section presents a candidate model
for supernova surveys that has the fidelity needed for the photometric
supernova analysis of the Dark Energy Survey and the Large Synoptic Survey Telescope.
This model captures the current treatment in current analysis but expanded to include
photometry-only transients.  This may not be the ultimate model used, indeed many models
need to be considered for model testing.

The Probabilistic Graphical Model is shown in Figure~\ref{pgm:fig}. The underlying behavior of the universe is described by the following elements:
\begin{description}
\item [Cosmology] Luminosity distance for the cosmological model being considered,
e.g.\ a $wCDM$ universe parameterized by $\Omega_M$, $\Omega_w$, $w_0$, $w_a$.
\item[SNe~Ia, Non-Ia Populations] Time-dependent luminosity for all transient populations
that may enter
the analysis.  The SALT2 model is a candidate for SNe~Ia, with parameters $\alpha$, $\beta$,
and pdf's for $x_1$ and $c$.  The PSNID treatment of non-Ia's is a candidate for the other
transients.
\item [Relative Rates] Relative rates of all the transients populations under consideration.  The
model could be extended to measure absolute rates, but that is unnecessary if
the cosmological parameters are the goal.
\end{description}
Each transient is described by the following elements:
\begin{description}
\item[Host Galaxy] The host galaxy, or more generally for the case of hostless supernovae,
the environment from which the transient arises.  The host is described by its redshift
and parameters that may be correlated with Hubble diagram residuals, such as mass,
specific star formation rate, metallicity.
\item[Type Subtype] Specification of the the transient: which population to which it belongs
and its internal parameters.  For example, an object could be SN~Ia with specific
values for its SALT2 parameters $c$, $x_1$, $t_0$ and its realization
from the error snake.  This dependent on the relative rates and
its host galaxy including redshift.
\item[Distance] Distance modulus or equivalently the luminosity distance of the host galaxy,
which in our model corresponds to the cosmological redshift of the transient.  The value
is fixed based on the cosmological model and redshift.
\end{description}
The individual photometric measurements of a transient are described by the following
elements:
\begin{description}
\item[Luminosity]  Luminosity as a function of wavelength
corresponding to the date of observation.   This depends on the population, type,
and subtype.  Given evidence for correlations between host properties and Hubble
residuals, a direction connection between host galaxy and luminosity is made.
\item[Flux] Flux of the transient incident to earth at the date of observation.  It is 
fixed based on the luminosity, redshift, and distance.
\end{description}
The observatory is described by the following element:
\begin{description}
\item[Throughput] The transmission function for the band at that date appropriate
for the transient.  A simple parameterization could be calibration zeropoints; more
sophisticated descriptions can vary the shape, not only the normalization, of the
transmission.
\end{description}
The data subscripted by ``o'' are
\begin{description}
\item[$\text{Photometry}_o$] Photometric flux measurement.  The expected measurement
is the incident flux integrated over the throughput.  Typically the measurement
uncertainties are from a Poisson distribution.  In practice, photometric data extraction
is performed in an independent analysis that isolates the transient flux
from contaminating background light. 
\item[$\text{Type Subtype}_o$] Measurement of the intrinsic transient type.  This is done
through spectroscopy.
\item[$\text{Redshift}_o$] Measurement of the host redshift.  The redshift can be
spectroscopic or photometric.  Uncertain host galaxy identification contribute
to measurement errors.
\item[$\text{Host Properties}_o$] Measurement of the host properties such
as mass, sSFR, metallicity. Uncertain host galaxy identification contribute
to measurement errors.
\end{description}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6.5in]{/Users/akim/project/abc/results/hdpgm.pdf} 
   \caption{Probabilistic Graphical Model for the SN~Ia analysis.  
   The forward modeling
   flow goes from top to bottom, starting with the description of the universe, observatory,
   and data.    A transient occurs in host galaxy $g_i$.  The type $T$ depends on the
   host and relative rates $r$.  The transient parameters $\theta$ depend on the
   transient model $\Theta$ and the host.  The luminosity $L$ depends on the preceding
   parameters.  
   A model with parameters $\Omega_M$ and $w$ fix the distance modulus $\mu_i$.
   The 
   incoming photon flux $f$  are then fixed
   with host redshift and distance modulus.
   The measured light curve depends on the instrumental throughput $Z$.  There are
   spectroscopic
   measurements $\theta_S$, $T_S$, $z_S$ of the transient parameters, type, and
   redshift.  $G$ is the determination of the host galaxy from photometric data.
   \label{pgm:fig}}
\end{figure}

This hierarchical model has several features worth noting.  Transients with and without
spectroscopic classification are treated together: those with classification help constrain
the properties of the underlying population to inform the treatment of those without.
Photometric classification is treated internally, through the
latent Type.  The system throughput is treated as a probabilistic variable
allowing for self-calibration; this could be omitted from the model with calibration applied
to the Photometry measurements.  Host-galaxy misclassification enters as measurement
uncertainties.  Malmquist bias and other selection effects do not appear explicitly, but are accounted
for in the likelihoods.  The model could be extended to include summary statistics,
for example the results of an external supernova classifier; the use
of summary statistics would affect the manner in which the model is evaluated
due to our inability to write their likelihoods.

\subsection{Sample Selection}
The transients that enter the analysis satisfy some selection criteria.  Trivially, they
have to be discovered in the first place and often more stringent photometric signal-to-noise
requirements are applied.  Additionally, the probability for a transient to have successful
spectroscopy may depend on parameters.
These criteria have not yet been determined/selected
(Argonne for photometry, OzDES/Ryan for spectroscopy are candidates to do this);
presented here is a sketch of the likelihood calculation for a reasonable
photometric selection criterion.

For each transient $\nu$, the criterion is to have $\ge N$ photometric points
above a signal-to-noise threshold given $M_\nu$ available measurements:
every photometric point is associated with a flux threshold that it either passes
or fails.  Given a total $M=\sum_\nu M_\nu$ data points, there are
$2^M$ possible combinations
of passing or failing theshold, of which only
$\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}$  combinations would lead to
the inclusion of the transients in the sample.

The probability distribution function for all possible data realizations can be written
as the sum of the pdf's of all possible permutations
\begin{equation}
p(data|model) = \sum_{k=1}^{2^M} p(data, b_k| model),
\label{likelihood_u:eqn}
\end{equation}
where $b$ contains all possible combinations.
The probability distribution function for all possible data realizations that pass
our selection criteria is a conditional pdf. It is proportional to the underlying
pdf after removal of conditions that are not achieved, i.e.\ removal from the sum
in Eqn.~\ref{likelihood_u:eqn} of all combinations that do not meet the sample
selection criteria. This leaves a reduced set $b$ of
possible permutations
\begin{equation}
\mathcal{L}(data|\mathcal{S}, model) \propto \sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} p(data, b_k| model),
\end{equation}
where $\mathcal{S}$ is the sample-selection condition.

@@

Assembling this together, the likelihood is
\begin{equation}
\mathcal{L}(data|\mathcal{S}, model) = \frac{\sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} \epsilon(Photometry_o, b_k)p(data| model)}{\int ddata\,
\sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} \epsilon(Photometry_o, b_k)p(data| model)
}
\end{equation}
where the normalizing factor is included explicitly as a reminder that it has 
parameter dependence and must not be neglected in calculations.

Consider the traditional case of Malmquist bias of a single object,
where a single measurement has
to be above flux threshold.  For the underlying distribution with no flux threshold there
are $2^1=2$ possible configurations, the flux is either above or below threshold.  For
the sample distribution, there is $\binom{1}{1}=1$ possible configuration: the flux
is above threshold.   The likelihood for the measured flux is the truncated version
of the underlying distribution.

For the case of a single object with two measurements and a single threshold requirement,
there are $2^2=4$ possible configurations of which $\sum_{k=1}^{2} \binom{2}{k}=3$
would allow sample selection, the exception being when both measurements fall below threshold.
The likelihood for each flux is composed from
the sum of three truncated distributions of which one accepts faint fluxes,
resulting in resultant likelihoods that do not fall to zero below detection threshold.

\subsection{Underlying Likelihood}
The likelihood of the analysis sample is calculated from the underlying pdf of data.  Based on Figure~\ref{pgm:fig},
\begin{align}
p(data|model) &=\int dType\, dLuminosity\, p(Photometry_o |  Luminosity, Cosmology,Host,Throughput)  \nonumber\\
& p(Luminosity| Type
, Host, Population) p(Type | Rates, Host)  \nonumber\\
& \times \int dType\, p(Type_0|Type) p(Type|Rates, Host) \nonumber \\
& \times p(Redshift_o, Host_o| Host)
\label{like:eqn}
\end{align}
where $data=\{Photometry_o, Type_o, Redshift_o, Host_o\}$,
$model=\{Cosmology, Populations, Rates\}$, and we anticipate the independence
of photometric and spectroscopic typing measurements.

Now for specificity candidate models for the pdf's that enter Eqn.~\ref{like:eqn}
are presented.
\begin{itemize}
\item The type is drawn from the host-dependent relative rate between SNe~Ia and non-Ia's 
\begin{equation}
Type | Rates, Host \sim {\rm Bernoulli}(\pi(z;r)),
\end{equation}
where $\pi$ is a model for the relative rate of SNe~Ia as a
function of galaxy redshift $z$.  {\bf A reasonable choice for $\pi$ needs to be
selected.}

@@

Models for non-Ia supernovae need to be selected.  The model used in PSNID is a good
place to start.
\item The underlying SED of transients.  For SNe~Ia the SALT2 model
is an option, although new models that separate dust and intrinsic color or
identify new SN~Ia parameters are expected in the near future.  Absolute magnitudes
that depend on host-galaxy properties need to be considered. 
\begin{equation}
Luminosity| Type
, Host, Population \sim L_{SALT2}\left(\frac{t-t_0}{1+z}; \alpha, \beta, x_1, c\right) \exp{\left(\delta_G\mathcal{H}(g)\right)},
\end{equation}
where the first  term is the SALT2 light-curve and absolute magnitude
model with error snake.  Possible host-galaxy effects like the ``mass step'' are
accounted in $\mathcal{H}(g)$ where $g$ is the corresponding host parameter
and $\delta_G$ is the size of the offset.  The host redshift is $z$.

@@

The expected photometric signal in counts depends on the flux and throughput of the
optical chain.  A first model encapsulates flux calibration through a zeropoint
\begin{equation}
counts(Throughput, f) = 10^{Z/2.5} \int  f(\lambda) T_0(\lambda)d\lambda,
\end{equation}
where $T_0$ is a fiducial transmission function for the appropriate filter.  A more sophisticated
analysis can have a transmission function specific to each observation.

Practically the photometric extraction is handled by independent software, which calculates
the $n$ with uncertainties $C_P$
by modeling and separating out polluting background light from the transient
signal
\begin{equation}
Photometry_o |  Luminosity, Cosmology,Host,Throughput \sim \mathcal{N}(counts,C_P).
\end{equation}
Dillon is providing this.
Note that the model has explicit calibration parameters that are to be fit.  An alternative
approach is to include calibration uncertainties in $C_P$.

Recall that the sample likelihood has terms
$\epsilon(Photometry_o, b_k)p(data| model)$, which turn out to be truncated Gaussians.

\item Spectroscopic measurements are assumed
to provide prefect determinations of transient type
\begin{equation}
Type_o | Type  \sim \delta(Type-Type_o).
\end{equation}
\item There are measurements of the host galaxy properties.
The first complication is
the correct identification of the host.  For transients that have spectroscopic
confirmation, an unambiguous host determination is assumed such that
\begin{align}
Redshift_o  | Host & \sim \delta(Redshift_o- z)\\
Host~properties_o  | Host & \sim \mathcal{N}(p, C),
\end{align}
where $p$ are the Host properties being measured,
$C$ is the covariance of the measurement of the galaxy identified as the host.
DES plans to get spectroscopic redshifts with negligible measurement uncertainties on all
possible hosts.

For the photometric sample, there is uncertainty in the identity of the host galaxy.
From a set of potential host galaxies $\hat{G}$ each with probability $\pi$ of being the correct host,
\begin{equation}
G \sim \prod_i \delta(G-\hat{G}_i) \pi_i.
\end{equation}
Ravi can provide for each transient a list of candidate hosts and their probabilities.
Thus for the photometric sample
\begin{align}
Redshift_o  | Host &  \sim \sum_i \pi_i \delta(Redshift_o- z_i)\\
Host~properties_o  | Host & \sim  \sum_i \pi_i \mathcal{N}(p_i, C),
\end{align}
\end{itemize}

@@

\subsection{Likelihoods}
The transients are divided into
the following subsets:
{\it obs} are transients observed spectroscopically while active, from which $T_S=1$ are those typed
as SN~Ia and $T_S=0$ as non-Ia.  {\it mis} transients are not observed
spectroscopically when active.  The data from each subset have different forms for their likelihood.
The  {\it obs} sample constrains and specifies the parameter distributions of the 
parameters missing from the {\it mis} sample.

\subsubsection{Likelihood for the {\it obs} Set}
%\begin{multline}
%p(n_{SN}, G |  \Omega_M, w, \theta_r, \alpha_{Ia}, \beta_{Ia},\sigma_{Ia}, \alpha_{\mathit{non-Ia}},\beta_{\mathit{non-Ia}}, \sigma_{\mathit{non-Ia}},  Z, g, g_N, f_g)\\
%= \sum_i \int_L dL\, p(n_{SN}, G | b_i, L, \ldots)
%P(b_{i} |L, \ldots) P(L|\ldots) ,
%\end{multline} 
%\begin{equation}
%p(n_{SN}, G | b_i, L, \ldots)
%  =  \frac{ \prod_j
% \epsilon(n_{SN,j}; b_{ij})
%  p(n_{SN}, G | L, \ldots)}
%  {\prod_j P(b_{ij}{ |L,\dots)}}.
%\label{misconf:eqn}
%\end{equation}

\section{Tasks}
\begin{table}[htdp]
\caption{default}
\begin{center}
\begin{tabular}{|c|c|}
\hline
Task/Deliverable & Responsible \\ \hline
Model Design & \\
Sampler &\\
Photometric Selection &\\
Spectroscopy Selection &\\
Host Galaxy Association &\\
Host Galaxy Parameters &\\
SN~Ia Models Selection &\\
Non-Ia Models Selection &\\
SN light curves ($n$) &\\
Photometric Zeropoints &\\
\hline
\end{tabular}
\end{center}
\label{Tasks and Responsible Parties}
\end{table}%

\section{Misc}
The simulation of data from the model presented in
and their analysis is implemented in Python and are available
on GitHub\footnote{{git@github.com:AlexGKim/abc.git}}.

>>>>

\section{DES SN Survey Model}
\label{snIamodel:sec}
\subsection{Model}
\label{model:sec}
This Section presents a candidate model
for supernova surveys that has the fidelity needed for the photometric
supernova analysis of the Dark Energy Survey and the Large Synoptic Survey Telescope.
This model captures the current treatment in current analyses but expanded to include
photometry-only transients.  This may not be the ultimate model used, indeed many models
need to be considered for model testing.

The Probabilistic Graphical Model is shown in Figure~\ref{pgm:fig}. The underlying behavior of the universe is described by the following elements:
\begin{description}
\item [Cosmology] Luminosity distance for the cosmological model being considered,
e.g.\ a $wCDM$ universe parameterized by $\Omega_M$, $\Omega_w$, $w_0$, $w_a$.
\item[SNe~Ia, Non-Ia Populations] Time-dependent luminosity for all transient populations
that may enter
the analysis.  The SALT2 model is a candidate for SNe~Ia, with parameters $\alpha$, $\beta$.  The PSNID treatment of non-Ia's can be made into a model for the other
transients.
\item [Relative Rates] Relative rates of all the transients populations and
subpopulations (e.g. SALT2 $x_1$, $c$) under consideration.  The
model could of been extended to measure absolute rates, but that is unnecessary if
the cosmological parameters are the goal.
\end{description}
Each transient is described by the following elements:
\begin{description}
\item[Host Galaxy] The host galaxy, or more generally for the case of hostless supernovae,
the environment from which the transient arises.  The host is described by its redshift
and other parameters that may be of interest such as mass,
specific star formation rate, metallicity.
\item[Type Subtype] Specification of the the transient: the population to which it belongs
and its internal parameters.  For example, an object could be SN~Ia with specific
values for its SALT2 parameters $c$, $x_1$, $t_0$ and its random dispersion
realization (both absolute magnitude and from the error snake). 
This is dependent on the relative rates and
its host galaxy including redshift.
\item[Distance] Distance modulus or equivalently the luminosity distance of the host galaxy,
which in our model corresponds to the cosmological redshift of the transient.  The value
is fixed based on the cosmology and redshift.
\end{description}
The individual photometric measurements of a transient are described by the following
elements:
\begin{description}
\item[Luminosity]  Luminosity as a function of wavelength
corresponding to the date of observation.   This depends on the population, type,
and subtype.  Given evidence for correlations between host properties and Hubble
residuals, a direction connection between host galaxy and luminosity is made.
\item[Flux] Flux of the transient incident to earth at the date of observation.  It is 
fixed based on the luminosity, redshift, and distance.
\end{description}
The observatory is described by the following element:
\begin{description}
\item[Throughput] The transmission function experienced by the transient during
the observation.  It depends on band, position on the focal plane, and date of observation.
\end{description}
The data (subscripted by ``o'' for observation)  are:
\begin{description}
\item[$\text{Photometry}_o$] Photometric flux measurement of the transient.
The expected measurement
is the incident flux integrated over the throughput.
\item[$\text{Type Subtype}_o$] Spectroscopic
measurements of the intrinsic transient type.  It is dependent on the underlying
type.
\item[$\text{Redshift}_o$] Measurement of the host redshift.  The redshift can be
spectroscopic or photometric.  It is dependent on the host redshift, and
redshifts of any other galaxies that may be confused as the host (not shown explicitly
in the PGM).
\item[$\text{Host Properties}_o$] Measurement of the host properties such
as mass, sSFR, metallicity. It is dependent on the host galaxy, and
any other galaxies that may be confused as the host.
\end{description}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=6.5in]{/Users/akim/project/abc/results/hdpgm.pdf} 
   \caption{Probabilistic Graphical Model for the SN~Ia analysis.  
   The description of the elements and dependencies of the model are given in
   \S\ref{model:sec}.
   \label{pgm:fig}}
\end{figure}

This hierarchical model has several features worth noting.  Transients with and without
spectroscopic classification are treated together: those with classification help constrain
the properties of the underlying population to inform the treatment of those without.
Photometric classification is treated internally, through the
latent Type.  The system throughput is treated as a probabilistic variable
allowing for self-calibration; this could be omitted from the model with calibration
and its uncertainties applied
to the Photometry measurements.  Host-galaxy misclassification enters as measurement
uncertainties.  Malmquist bias and other selection effects do not appear explicitly, but are accounted
for in the likelihoods.  The model could be extended to include summary statistics,
for example the results of an external supernova classifier; the use
of summary statistics would affect the manner in which the model is evaluated
due to our inability to write their likelihoods.

\subsection{Sample Selection}
The transients that enter the analysis satisfy some selection criteria.  Trivially, they
have to be discovered in the first place and often more stringent photometric signal-to-noise
requirements are applied.  Additionally, the probability for a transient to have successful
spectroscopy may be dependent on model parameters.

Sample selection criteria for DES have not yet been finalized
(Argonne for photometry, OzDES/Ryan for spectroscopy are candidates to do this);
presented here is a sketch of the likelihood calculation for a reasonable
photometric selection criterion:
for each transient $\nu$, the criterion is to have $\ge N$ photometric points
above a signal-to-noise threshold given $M_\nu$ available measurements.
Each photometric point is associated with a flux threshold that it either passes
or fails.  Given a total $M=\sum_\nu M_\nu$ data points, there are
$2^M$ possible configurations
of passing or failing theshold, of which only
$\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}$  configurations lead to
the inclusion of the transients in the sample.

The likelihood for the analysis
sample is the conditional distribution obtained by applying the selection criteria
on the domain of the likelihood given no selection criteria.  This latter likelihood
can be written
as the sum of the contributions from all possible threshold-passing configurations
\begin{equation}
p(data|model) = \sum_{k=1}^{2^M} p(data, \hat{b}_k| model),
\label{likelihood_u:eqn}
\end{equation}
where $\hat{b}$ is the set containing all possible configurations.
Let $b$ be the subset of $\hat{b}$ 
that satisfies sample selection. Then the selection criteria is $\mathcal{S} = \hat{b}_k
\in b$.
The likelihood of the analysis sample is thus proportional to Eqn.~\ref{likelihood_u:eqn}
with failing configurations removed
\begin{equation}
\mathcal{L}(data|\mathcal{S}, model) \propto
\sum_{k=1}^{2^M} p(data, \hat{b}_k| \hat{b}_k
\in b, model) = \sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} p(data, b_k| model).
\end{equation}

@@

Assembling this together, the likelihood is
\begin{equation}
\mathcal{L}(data|\mathcal{S}, model) = \frac{\sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} \epsilon(Photometry_o, b_k)p(data| model)}{\int ddata\,
\sum_{k=1}^{\prod_\nu \sum_{k=N}^{M_{\nu}} \binom{M_{\nu}}{k}} \epsilon(Photometry_o, b_k)p(data| model)
}
\end{equation}
where the normalizing factor is included explicitly as it has 
parameter dependence and must not be neglected in calculations.

Consider the traditional case of Malmquist bias of a single object,
where a single measurement has
to be above flux threshold.  For the underlying distribution with no flux threshold there
are $2^1=2$ possible configurations, the flux is either above or below threshold.  For
the sample distribution, there is $\binom{1}{1}=1$ possible configuration: the flux
is above threshold.   The likelihood for the measured flux is proportional to the original
distribution truncated so that fluxes below threshold are assigned zero probability.

For the case of a single object with two measurements of which only one is needed to
pass threshold,
there are $2^2=4$ possible configurations of which $\sum_{k=1}^{2} \binom{2}{k}=3$
allow sample selection, the exception being when both measurements fall below threshold.
The likelihood for each flux is composed from
the sum of three truncated distributions of which one accepts faint fluxes,
resulting in likelihoods that are not zero below detection threshold.

\subsection{Underlying Likelihood}
The likelihood of the analysis sample is calculated from the underlying pdf of data.  Based on Figure~\ref{pgm:fig},
\begin{align}
p(data|model) &=\int dType\, dLuminosity\, p(Photometry_o |  Luminosity, Cosmology,Host,Throughput)  \nonumber\\
& p(Luminosity| Type
, Host, Population) p(Type | Rates, Host)  \nonumber\\
& \times \int dType\, p(Type_0|Type) p(Type|Rates, Host) \nonumber \\
& \times p(Redshift_o, Host_o| Host),
\label{like:eqn}
\end{align}
where $data=\{Photometry_o, Type_o, Redshift_o, Host_o\}$,
$model=\{Cosmology, Populations, Rates\}$, and the independence
of photometric and spectroscopic typing measurements is anticipated.

For specificity candidate models for the pdf's that appear in Eqn.~\ref{like:eqn}
are now presented.
\begin{itemize}
\item The type is drawn from the host-dependent relative rate between SNe~Ia and non-Ia's 
\begin{equation}
Type | Rates, Host \sim {\rm Bernoulli}(\pi(z;r)),
\end{equation}
where $\pi$ is a model for the relative rate of SNe~Ia parameterized by $r$ as a
function of galaxy redshift $z$.  {\bf A reasonable choice for $\pi$ needs to be
selected.}

@@

Models for non-Ia supernovae need to be selected.  The model used in PSNID is a good
place to start.

Note that the rates may not have been important in spectroscopic analyses, but are important here to help infer the types/subtypes of transients without
a spectrum.
\item For the underlying SED of transients for SNe~Ia the SALT2 model
is an option, although new models are expected to appear shortly.  Absolute magnitudes
that depend on host-galaxy properties also need to be considered. 
In the SALT2 context,
\begin{equation}
Luminosity(Type
, Host, Population)= L_{SALT2}\left(\frac{t-t_0}{1+z}; \alpha, \beta, x_1, c\right) \exp{\left(\delta_G\mathcal{H}(g)\right)},
\end{equation}
where the first  term is the SALT2 light-curve and absolute magnitude
model with error snake.  Possible host-galaxy effects like the ``mass step'' are
accounted in $\mathcal{H}(g)$ where $g$ is the corresponding host parameter
and $\delta_G$ is the size of the offset.  The host redshift is $z$.
Note that for this model the parameter is fixed, though
generally this may not be the case.

@@

The expected photometric signal in counts depends on the flux and throughput of the
optical chain.  A simple model encapsulates flux calibration through a zeropoint $Z$
and $T_0$  a fiducial transmission function for the appropriate filter.
More
sophisticated descriptions of calibration can vary the shape, not only the normalization, of the
transmission.  For the simple model,
\begin{equation}
counts(Throughput, f) = 10^{Z/2.5} \int  f(\lambda) T_0(\lambda)d\lambda.
\end{equation}

Practically the photometric extraction is handled by independent software, which calculates
the integrated counts with uncertainties $C_P$
by modeling and separating out polluting background light from the transient
signal
\begin{equation}
Photometry_o |  Luminosity, Cosmology,Host,Throughput \sim \mathcal{N}(counts,C_P).
\end{equation}
Dillon is providing this $Photometry_o$ and $C_P$.

An alternative model would be to remove Throughput
and include calibration uncertainties in $C_P$.  This would be a huge covariance
matrix!
\item Spectroscopic measurements are assumed
to provide prefect determinations of transient type
\begin{equation}
Type_o(Type)  = Type.
\end{equation}
\item There are measurements of the host galaxy properties.
For transients that have spectroscopic
confirmation, an unambiguous host determination is assumed such that
\begin{align}
Redshift_o(Host) & = z\\
Host~properties_o  | Host & \sim \mathcal{N}(p, C),
\end{align}
where $p$ are the Host properties being measured
and
$C$ their measurement uncertainty.

For the photometric sample, there is uncertainty in the identity of the host galaxy.
Suppose host-galaxy identification gives
a set of potential hosts $\hat{G}$ each with probability $\pi$ of being the correct host,
what Ravi is doing.
Then for the photometric sample
\begin{equation}
p(Redshift_o, Host~properties_o   | Host) = \sum_i \pi_i \delta(Redshift_o- z_i)\mathcal{N}(Host~properties_o-p_i, C)).
\end{equation}
Recall that DES plans to get spectroscopic redshifts with negligible measurement uncertainties on all
possible hosts.
\end{itemize}

@@

\section{Tasks}
Here are a list of initial tasks and ingredients needed to proceed.
\begin{itemize}
\item Determination of flux thresholds for each photometric point given
a $S/N$ threshold
\begin{equation}
threshold(point, S/N).
\end{equation}
If we work in the sky-noise dominated regime, I believe this information is already
calculated by DM.
\item Identification of selection criteria for spectroscopic success, as a function
of data.
\item A rates model for transient types and subtypes
\begin{equation}
\pi(z;r).
\end{equation}
\item Decision on how to model the distribution of $x_1$ and $c$.  For a first try a
single normal distribution seems sufficient but do we want to be more ambitious?
\item A non-Ia transient model.  Much of its usage is in classification, so the PSNID
description is a place to start.
\item Calibration model and uncertainties. Assuming we work with zeropoints
$p(Z)$ is needed.
\item Data! Spectroscopic Type and uncertainties, Spectroscopic redshifts and
uncertainties, galaxy properties and uncertainties, host-galaxy associations
and uncertainties, photometry and uncertainties.
\item Determine the mechanics of doing the analysis.  A Bayesian MCMC could produce posteriors, which sampler that best suits our needs? Is a frequentist
analysis technically unfeasible? If redshifts were free to wander I would think so, but maybe
it is possible in this model.
\end{itemize}

%\section{Misc}
%The simulation of data from the model presented in
%and their analysis is implemented in Python and are available
%on GitHub\footnote{{git@github.com:AlexGKim/abc.git}}.
